\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubheadingtwo}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}





\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{thetathya.github.io/}{\Large Tathya Thakar}} & Email : \href{mailto:tathyathaker5@gmail.com}{tathyathaker5@gmail.com}\\
  \href{https://www.linkedin.com/in/thetathya}{linkedin.com/in/thetathya} & Mobile : +1-516-707-5254 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Texas at Dallas}{Dallas, TX}
      {Master of Science in Computer Science}{Jan. 2021 -- Jan. 2023}
    \resumeSubheading
      {Gujarat Technological University}{Ahmedabad, India}
      {Bachelor of Engineering in Computer Engineering;  GPA: (8.28/10.0)}{Aug. 2016 -- Sep. 2020}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------

\section{Experience}
  \resumeSubHeadingListStart
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

 
    \resumeSubheading
      {Rudra Automation Pvt. Ltd.}{Ahmedabad, India}
      {Web Developer}{Jun 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{Development and Integration}
          {Developed features like checkout process, order returns, functionality for Back-office staff and implemented payment integration for various gateway and more for e-commerce store.}
        \resumeItem{Testing}
          {Wrote test scripts and tested website on different platforms to maintain the design.}
        \resumeItem{Documentation}
          {Ensuring proper documentation and reports in all stages of product life cycle.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------Leadership Experience-----------------

\section{Leadership Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Gujarat Industrial Hackathon}{Government of Gujarat}
        {Team Leader}{Jan 2019 - Mar 2019}
        \resumeItemListStart
        \resumeItem{Project}
        {To help companies, libraries and other institution to know precisely what users are reading and how efficient are they at reading by providing detailed statistics.}
        \resumeItem{Teamwork}
        {Supervised a team of 5 people to work on the project and streamlined the development to deliver on time.}
        \resumeItem{Statistics}
        {Over 1000 Teams participated (6000+ participant) and we secured 2nd Rank in the Hackathon. Got the award from the Honorable Minister of State Education.}
        \resumeItemListEnd
        
        \resumeSubheading
        {Gujarat Technological University}{Government of Gujarat}
        {Event Coordinator}{Jan 2019 - Mar 2019}
        \resumeItemListStart
        \resumeItem{Leadership}
        {I was part of the Management team where I lead the Computer Engineering Department. From the Flyers to Decoration, from making the Questions for Event to manage volunteers, I supervised all the event related things with an incredible team with team spirit and contribution.}
        \resumeItem{Teamwork}
        {On 6th and 7th of March 2019 the event was hosted. After 2 Months of hard work and unparalleled contribution from Team. It resulted in one of the best events of our Institute with highest participants in the history of our Institute.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd








%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{SuperResolution}
      {Created a Deep Learning model that uses Computer Vision to enhances low resolution images up to 4 times. The model was trained on over 10,000 image data set containing both high and low-resolution images. With the help of Generative Adversarial Network, the model was trained to become more accurate in generating high resolution images.\newline Skills used: Python, Computer Vision, TensorFlow, CNN, GAN, NumPy, Matplotlib}
    
    \resumeSubItem{Portuguese Bank Campaign Prediction}
      {Goal was to find the vital feature to use in the next telemarketing campaign by learning from the previous campaign. Predicting the success and find role playing features of the users of the campaign based on past telemarketing data.\newline Skills used: Python, Sklearn, Pandas, NumPy, Matlpotlib}
      
    \resumeSubItem{\href{https://github.com/thetathya/Face_Mask_Detector}{Face Mask Detector}}
      {The project is built using Computer Vision and Deep Learning concepts in order to detect face masks in live video streams. The model uses the MobileNetV2 architecture which is computationally efficient which allows it deploy on embedded systems easily like Raspberry Pi, Google Coral, etc. \newline Skills used: MobileNetV2, Python, Computer Vision, TensorFlow, NumPy, Matplotlib, Deep Learning}
  \resumeSubHeadingListEnd



%-----------Independent Coursework-----------------

\section{Independent Coursework}
  \resumeSubHeadingListStart

    \resumeSubheadingtwo
      {Google Cloud Baseline: Machine Learning, Artificial Intelligence: Qwiklabs}{May 2019}


    \resumeSubheadingtwo
      {Google Cloud Platform Essentials: Qwiklabs}{May 2019}

    % \resumeSubheading
    %   {Applied Data Science with Python by University of Michigan}{}
    %   {Coursera}{March 2019}
    %   \resumeItemListStart
    %     \resumeItem{Introduction to Data Science in Python}
    %       {December 2017}
    %     \resumeItem{Applied Plotting, Charting and Data Representation in Python}
    %       {January 2018}
    %     \resumeItem{Applied Machine Learning in Python}
    %       {August 2018}
    %     \resumeItem{Applied Text Mining in Python}
    %       {February 2019}
    %     \resumeItem{Applied Social Network Analysis in Python}
    %       {March 2019}
    %   \resumeItemListEnd
      
      \resumeSubheadingtwo
      {Applied Data Science with Python by University of Michigan: Coursera}{March 2019}
      \resumeItemListStart
        \resumeItem{Courses}
          {Introduction to Data Science in Python, Applied Plotting, Charting and Data Representation in Python, Applied Machine Learning in Python, Applied Text Mining in Python, Applied Social Network Analysis in Python}
      \resumeItemListEnd
    
    \resumeSubheadingtwo
      {Machine Learning by Stanford University: Coursera}{May 2018}
    
    \resumeSubheadingtwo
      {The Complete JavaScript Course for Web Development Beginners: Udemy}{October 2017}
    
    \resumeSubheadingtwo
      {Data Structure and Algorithms in Python by IIT-Madras: NPTEL}{September 2017}
    
    \resumeSubheadingtwo
      {The Complete Python Course: Udemy}{February 2017}
    
    \resumeSubheadingtwo
      {Android Full Stack Development and Android Wearable: IEEE}{June 2016}

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
    \resumeSubHeadingListStart
        \resumeSubItem{Languages}
        {Scala, Python, Javascript, C++, SQL, Java}
        
        \resumeSubItem{Technologies}
        {Android Studio, Hadoop, AWS}
        
        \resumeSubItem{Operating Systems}
        {UNIX, Windows, MacOS, Linux}
        
        \resumeSubItem{Databases}
        {Oracle, MongoDB, PostgreSQL, MySql}
        
        \resumeSubItem{Framework and Tools}
        {OpenCV, TensorFlow, Sklearn, Bootstrap, Pandas, NumPy, Matplotlib, Django, Flask}
    \resumeSubHeadingListEnd
%     \item{
%       \textbf{Languages}{: }
%     }
%     \item{
%         \textbf{}{: }
%     }
%   \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}